Primal-dual algorithm for computing Nash equilibria in sequential games with imcomplete information

### 2014-12-15 nips2015.tex
more enh

\author{
DOHMATOB Elvis}
%% \institute{Parietal team, Inria Saclay Ile-de-France\\
%% Saclay, France\\

\title{Primal-dual algorithm for computing Nash equilibria in
% two-person zero-sum
sequential games
% with imcomplete information and perfect recall
}

@@

\begin{abstract}
We present a simple $\mathcal{O}(1/\epsilon)$ primal-dual algorithm with a low cost per iteration, for computing Nash equilibria in two-person zero-sum sequential games like Texas Hold'em Poker. %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequence-form representation von Stengel's \cite{von1996efficient}
Our algorithm derives from the primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to the saddle-point problem corresponding to Nash equilibria. This limitation is due to the fact that the strategy profiles (polytopes) of players are sufficiently complex
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to prevent easy computation 
% (i.e using non-iterative procedures, etc.)
of euclidean
% (metric)%
 projections thereupon (the proximal operators).
Our technique is to dualize the linear constraints that form part of the player's strategy profile, thus obtainining an equivalent saddle-point problem which is more amendable to the primal-dual scheme. The resulting algorithm is simple, only involving matrix-vector multiplications
% (without any matrix inversions, etc.)
and nonnegative clipping.
% (taking point-wise max of a vector and 0)
The $\mathcal{O}(1/\epsilon)$ convergence rate of our algorithm derives explicitly from the general primal-dual algorithm in \cite{chambolle2010}. Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing}, our algorithm has a cheap and constant cost per iteration. As proof of concept, we apply our algorithm to solve Kuhn Poker.
\end{abstract}

@@

%%%
\paragraph{Sequence-form representaion}
The game consists of three players:
\begin{itemize}
\item player 1 (Alice),
\item player 2 (Bob), and
\item player 0, a special player called \textit{chance}, who plays a publicly known \textit{mixed strategy} $\beta_0$ (more on this later),
\end{itemize}
who take turns to play, according to the rules of the game. The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of moves) in the former.
The sequence-form representation for such a game is a quintuplet $(A, E_1, E_2, e_1, e_1)$, where
\begin{itemize}
\item For each \textit{information set} $h$ of player $k$, $\sigma_h$ is the sequence of moves to $h$. $C_h$ is the set of choices at $h$. $\mathcal{I}_k$ is the set of all information sets of player $k$, and the set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
\begin{equation}
\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
\end{equation}
Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the moves of all other players (the other player, and the \textit{chance} player, aka \textit{nature}) deleted. Such a sequence represents a possible sequence of moves made by player $k$ in the game, from start to finish.
\item Given a node $t$
  \begin{itemize}
  \item $a(t)$ is the payoff received by player $1$ at $t$. Note that $a(t)$ is $0$ for all nonleaf nodes.
  \item $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to a path in the game tree, by including the moves of the other players;
  \item $\beta_0(t)$ is the product of the probabilities of the moves made by the chance player along $\sigma_0(t)$.
  \end{itemize}

\item Besides nonnegativity, the \textit{realization plans} $z$ of each play $k$ have linear contraints of the form
\begin{equation}
    z_{\emptyset} = 1 \text{ and }
    z_{\sigma_h} = \sum_{c \in C_h}{z_{\sigma_h c}}\text{, } \forall h \in \mathcal{I}_k
  \label{eq:lin}
\end{equation}

@@

where $E_k$ a matrix with $p_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $p_k$-dimensional vector of the form $(1, 0, ..., 0)$. The \textit{strategy profile} of player $k$ is then the $n_k$-dimensional polytope
\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k}| z \ge 0\text{ and }E_kz = e_k\}
  \label{eq:poly}
\end{equation}

@@

\paragraph{Example of Nash equilibirum}
As an illustration, the pair $(x^*, y^*)$ given by
$x^* = (1, .478, .522, .174, .826)$ and
$y^* = (1, 1/2, 1/2)$ is a Nash equilibrium for the sequence-form game given by (not showing zero entries)\\
$A = \left(\begin{array}{ccc}
  &   &  \\
  &   &  \\
  & 1 & -1\\
  & -2 & 4\\
1 &   &  
\end{array}\right)$, $E_1 = \left(\begin{array}{ccccc}
  1 &   &   &   &  \\
  -1 & 1 & 1 &   &  \\
  -1 &   &   & 1 & 1
\end{array}\right)$,
$E_2 = \left(\begin{array}{ccc}
  1 &   &  \\
  -1 & 1 & 1
\end{array}\right)$, $e_1 = (1, 0, 0)$, and $e_2 = (1, 0)$.

\begin{remark}
  At least for sequential games, the matrices $A$, $E_1$, and $E_2$ are very large (can have upto billions of rows and columns) but very sparse too.
%% : $A$ will be sparse because a concrete sequential game will
%% typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
%% combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
%% $E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
%% zig-zag between only a limited number of the player's information sets so that a move at an information set will
%% rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
This sparsity should be thoroughly exploited by a solver for problem \eqref{eq:opt_pb}.
\end{remark}

@@

\section{Related work}
\label{sec:related_work}

Pending...

@@

\section{The algorithm}
We now derive our primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}. The algorithm is derived from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}. Though this scheme has recently gained considerable popularity in the signal processing community \cite{gramfort-etal:2013a}, to the best of our knowledge, this is the first time it is being applied to compute Nash equilibria.

@@

%% Theorem \ref{thm:pd}, can be interpreted as follows: 2 players $x$ (player 1)  and $y$ (player 2) go heads-on in a zero-sum game with payoff matrix $A$. Their strategy, profiles are $Q_1$ and $Q_2$ respectively, meaning that if player $j$ players a strategy which is outside $Q_k$ then they are panalized by inflicting an infinite loss yupon them. To remedy this, they recruit assistants $u$ and $v$, whose sole goal is to preven the ...
\begin{proof} First observe that $\forall (x, y) \in \mathbb{R}^{n_1} \times \mathbb{R}^{n_2}$, we have
  \begin{eqnarray*}
   -i_{Q_1}(x) = -i_{\mathbb{R}^{n_1}_+}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)},
      \end{eqnarray*}
  and
\begin{eqnarray*}
  i_{Q_2}(y) = i_{\mathbb{R}^{n_2}_+}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}
\end{eqnarray*}
  Thus,% problem \eqref{eq:opt_pb} is equivalent to
  \begin{eqnarray*}
    \begin{split}
  \underset{y \in Q_2}{min}\text{ }\underset{x \in Q_1}{max}\text{ }{x^TAy} &=
  \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\left(\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }
x^TAy - i_{Q_1}(x)\right) + i_{Q_2}(y) \\
&= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }x^TAy -i_{\mathbb{R}^{n_1}_+}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)} + i_{\mathbb{R}^{n_2}_+}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}\\
      &= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }\underset{v \in \mathbb{R}^{p_1}}{min}\text{ }\underset{u \in \mathbb{R}^{p_2}}{min}\text{ }x^TAy - x^TE_1^Tv + u^TE_2y + i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tv -(i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tu)\\
      &= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ } \underset{v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{u \in \mathbb{R}^{p_2}}{max}
      {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}\\
      &= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }
\underset{u \in \mathbb{R}^{p_2}}{max}
      {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}\\
      &=     \underset{y \in \mathbb{R}^{n_2}, v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{p_2}}{max}
           {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}
    \end{split}
  \end{eqnarray*}
where $K$, $G$, and $H$ are as given in \eqref{eq:things}.

Thus problem \eqref{eq:opt_pb} is equivalent to problem \eqref{eq:unconstrained_pb} as claimed.

About the proximal operators, indeed both $G$ and $F$ are separable sums of the indicator function of a convex set, whose prox is simply the euclidean projection operator onto the set,  and a linear transformation $z \mapsto a^Tz$ whose prox, at rank $\tau$, is simply $z \mapsto z - \tau a$.
\end{proof}
Now applying Algorithm 39 of \cite{chambolle2010} with $F := H^*$ (the \textit{convex conjugate} of $H$)
 to problem \eqref{eq:unconstrained_pb}, we obtain Algorithm \ref{Tab:algo_simplified} for solving the original problem \eqref{eq:opt_pb}. The $\mathcal{O}(1/\epsilon)$ convergence rate of Algorothm \ref{Tab:algo_simplified} hails directly from Theorem 1 of \cite{chambolle2010}. Note that this convergence rate cannot be improved in the framework of \cite{chambolle2010}, since neither $G$ nor $H$ is \textit{uniformly convex}.

@@

\section{Application to Poker: Kuhn Poker}
The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
$A = \left(\begin{array}{ccccccccccccc}
  &   &   &   &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
\end{array}\right)$,\\
$E_1 = \left(\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
\end{array}\right)$, $e_1 = e_2 = (1, 0, 0, 0, 0, 0, 0)$,\\
and $E_2 = \left(\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
\end{array}\right)$.\\
The pair $(x^*, y^*)$ of realization plans given by\\
$x^* = (1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725)$ and
$y^* = (1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1)$ is a Nash equlibrium for the game, computed using Algorithm  \ref{Tab:algo_simplified}. The convergence curve is shown in Fig \ref{Tab:conv_curves}. One easy checks that this equilibrium is feasible. Indeed,  $E_1x^* - e_1 = (4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67 \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, -8.62 \times 10^{-7}, -1.96 \times 10^{-5})$ and $E_2y^* - e_2 = (-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29 \times 10^{-6}, -1.50 \times 10^{-6}, 2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times 10^{-7})$. Finally, $x^*TAy^* = -0.055593685705289997$, which agrees to 4 d.p with the value of $-1 / 18$ computed analytically by Kuhn in his 1954 paper.

@@

\section{Generalization to general strategy profiles of a similar type}
Notice tha in \eqref{eq:poly}, the strategy profile of player $k$ can be factored as
\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k}_+| E_kz = e_k\text\}
\end{equation}

The framework presented sofar only demanded we be able to efficiently compute metric projections onto the nonnegative orthant $\mathbb{R}^{n_k}_+$ (nonnegative clipping). If we now consider general strategy profiles of the form
\begin{equation}
  Q_k := \{z \in C_k| E_kz = e_k\text\}
\end{equation}
where the $C_k$ are arbitrary convex sets for which the metric projections $\Pi_{C_k}$ can be effectively computed ...
\small
\bibliographystyle{ieeetr}
\bibliography{bib}

>>>>

\author{
Elvis DOHMATOB
\\
Parietal team, Inria Saclay Ile-de-France\\
Saclay, France\\
\textit{email}: firstname.lastname@inria.fr}

\title{Primal-dual algorithm for computing Nash equilibria in
% two-person zero-sum
sequential games with imcomplete information
% with imcomplete information and perfect recall
}

@@

\begin{abstract}
We present a simple $\mathcal{O}(1/\epsilon)$ primal-dual algorithm with a low cost per iteration, for computing Nash equilibria in two-person zero-sum sequential games like Texas Hold'em Poker. %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequence-form representation von Stengel's \cite{von1996efficient}
Our algorithm derives from the general primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to the saddle-point problem corresponding to Nash equilibria since the strategy profiles (polytopes) of players are so complex that it is not possible
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to analytically compute
% (i.e using non-iterative procedures, etc.)
euclidean
% (metric)%
 projections (the proximal operators) thereupon.
Our technique is to dualize the linear constraints that form part of the player's strategy profile, thus obtainining an equivalent saddle-point problem which is more amendable to the primal-dual scheme, without any additional overhead. The resulting algorithm is simple, only involving matrix-vector multiplications
% (without any matrix inversions, etc.)
and nonnegative clipping.
% (taking point-wise max of a vector and 0)
The $\mathcal{O}(1/\epsilon)$ convergence rate of our algorithm derives explicitly from the general primal-dual algorithm in \cite{chambolle2010}. Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing}, our algorithm has a cheap and constant cost per iteration. As proof of concept, we apply our algorithm to solve Kuhn Poker.
\end{abstract}

@@

%%%
\paragraph{From extensive-form to Sequence-form representaion}
The game consists of three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}, who plays a publicly known \textit{mixed strategy} $\beta_0$ (more on this later). All three players are treated symmetrically.
The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops. The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered moves) in the former.
The sequence-form representation for such a game is a quintuplet $(A, E_1, E_2, e_1, e_1)$, where
\begin{itemize}
\item At each node of the \textit{game tree}, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node. This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts.
\item Due to imcompleted information, each player's nodes are grouped into equivalent classes of strategically indistinguishable nodes called \textit{information sets}. $\mathcal{I}_k$ is the set of all information sets of player $k$. If each information set is a singleton, then the game reduces to a game complete information.
\item For each information set $h$ of player $k$, $\sigma_h$ is the sequence of moves to $h$. $C_h$ is the set of choices at $h$. The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
\begin{equation}
\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
\end{equation}
Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the moves of all other players (the other player, and the \textit{chance} player, aka \textit{nature}) deleted. Such a sequence represents a possible sequence of moves made by player $k$ in the game, from start to finish.
\item Given a node $t$
  \begin{itemize}
  \item $a(t)$ is the payoff received by player $1$ at node $t$. That the game is zero-sum means that player 2 receives a payoff of $-a(t)$. Note that $a(t)$ is $0$ for all non-leaf nodes.
  \item $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the moves of the other players;
  \item $\beta_0(t)$ is the product of the probabilities of the moves made by the chance player along $\sigma_0(t)$.
  \end{itemize}

\item Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
\begin{equation}
    z(\emptyset) = 1 \text{ and }
    z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0\text{, } \forall h \in \mathcal{I}_k
  \label{eq:lin}
\end{equation}

@@

where $E_k$ a matrix with $p_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $p_k$-dimensional vector of the form $(1, 0, ..., 0)$.

A realization plan $z$ for a player $k$ induces a behavioral strategy $\beta_k$ defined by
\begin{equation}
  \beta_k(c) := z(\sigma_hc)/z(\sigma_h)
\end{equation}
where $h \in \mathcal{I}_k$ and $c \in \mathcal{C}_h$, and $\beta_k(c)$ is the probability to play $c$ given that the player is at information set $h$.

The \textit{strategy profile} of player $k$ is then the $n_k$-dimensional polytope

\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k}| z \ge 0\text{ and }E_kz = e_k\}
  \label{eq:poly}
\end{equation}

@@

\paragraph{Example of Nash equilibirum}
As an illustration, the pair $(x^*, y^*)$ given by
$x^* = [1, .478, .522, .174, .826]^T$ and
$y^* = [1, 1/2, 1/2]^T$ is a Nash equilibrium for the sequence-form game given by (not showing zero entries)\\
$A = \left[\begin{array}{ccc}
  &   &  \\
  &   &  \\
  & 1 & -1\\
  & -2 & 4\\
1 &   &  
\end{array}\right]$, $E_1 = \left[\begin{array}{ccccc}
  1 &   &   &   &  \\
  -1 & 1 & 1 &   &  \\
  -1 &   &   & 1 & 1
\end{array}\right]$,
$E_2 = \left[\begin{array}{ccc}
  1 &   &  \\
  -1 & 1 & 1
\end{array}\right]$, $e_1 = [1, 0, 0]^T$, and $e_2 = [1, 0]^T$.

\begin{remark}
  The matrices $A$, $E_1$, and $E_2$ are very large (can have upto billions of rows and columns) but very sparse too.
%% : $A$ will be sparse because a concrete sequential game will
%% typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
%% combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
%% $E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
%% zig-zag between only a limited number of the player's information sets so that a move at an information set will
%% rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
This sparsity should be thoroughly exploited by a solver for problem \eqref{eq:opt_pb}.
\end{remark}

@@

\section{Related work}
\label{sec:related_work}
EGT used in \cite{hoda2010smoothing}...

@@

\section{The algorithm}
We now derive our primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}. The algorithm is derived from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}. Though this scheme has recently gained considerable popularity in the signal processing community
%\cite{gramfort-etal:2013a}
, to the best of our knowledge, this is the first time it is being applied to compute Nash equilibria.

@@

%% Theorem \ref{thm:pd}, can be interpreted as follows: 2 players $x$ (player 1)  and $y$ (player 2) go heads-on in a zero-sum game with payoff matrix $A$. Their strategy, profiles are $Q_1$ and $Q_2$ respectively, meaning that if player $j$ players a strategy which is outside $Q_k$ then they are panalized by inflicting an infinite loss yupon them. To remedy this, they recruit assistants $u$ and $v$, whose sole goal is to preven the ...
\begin{proof} First observe that $\forall (x, y) \in \mathbb{R}^{n_1} \times \mathbb{R}^{n_2}$, we have
  \begin{eqnarray*}
   -i_{Q_1}(x) = -i_{\mathbb{R}^{n_1}_+}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)},
      \end{eqnarray*}
  and
\begin{eqnarray*}
  i_{Q_2}(y) = i_{\mathbb{R}^{n_2}_+}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}
\end{eqnarray*}
  Thus,% problem \eqref{eq:opt_pb} is equivalent to
  \begin{eqnarray*}
    \begin{split}
  \underset{y \in Q_2}{min}\text{ }\underset{x \in Q_1}{max}\text{ }{x^TAy} &=
  \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\left(\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }
x^TAy - i_{Q_1}(x)\right) + i_{Q_2}(y) \\
&= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }x^TAy -i_{\mathbb{R}^{n_1}_+}(x) + \underset{v \in \mathbb{R}^{p_1}}{min}\text{}{v^T(e_1 - E_1x)} + i_{\mathbb{R}^{n_2}_+}(y) + \underset{u \in \mathbb{R}^{p_2}}{max}\text{}{u^T(E_2y - e_2)}\\
      &= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }\underset{v \in \mathbb{R}^{p_1}}{min}\text{ }\underset{u \in \mathbb{R}^{p_2}}{min}\text{ }x^TAy - x^TE_1^Tv + u^TE_2y + i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tv -(i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tu)\\
      &= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ } \underset{v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{u \in \mathbb{R}^{p_2}}{max}
      {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}\\
      &= \underset{y \in \mathbb{R}^{n_2}}{min}\text{ }\underset{v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}}{max}\text{ }
\underset{u \in \mathbb{R}^{p_2}}{max}
      {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}\\
      &=     \underset{y \in \mathbb{R}^{n_2}, v\in \mathbb{R}^{p_1}}{min}\text{ }\underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{p_2}}{max}
           {\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G(y, v) - H(x, u)}
    \end{split}
  \end{eqnarray*}
where $K$, $G$, and $H$ are as given in \eqref{eq:things}. Thus problem \eqref{eq:opt_pb} is equivalent to problem \eqref{eq:unconstrained_pb} as claimed.

About the proximal operators, indeed both $G$ and $F$ are separable sums of the indicator function of a convex set, whose prox is simply the euclidean projection operator onto the set,  and a linear transformation $z \mapsto a^Tz$ whose prox, at rank $\tau$, is simply $z \mapsto z - \tau a$.
\end{proof}
Now applying Algorithm 39 of \cite{chambolle2010} with $F := H^*$ (the \textit{convex conjugate} of $H$)
 to problem \eqref{eq:unconstrained_pb}, we obtain Algorithm \ref{Tab:algo_simplified} for solving the original problem \eqref{eq:opt_pb}. The $\mathcal{O}(1/\epsilon)$ convergence rate of Algorothm \ref{Tab:algo_simplified} hails directly from Theorem 1 of \cite{chambolle2010}.
\begin{remark}
  Note that the convergence rate of $\mathcal{O}(1/\epsilon)$ cannot be improved in the framework of \cite{chambolle2010}, since neither $G$ nor $H$ is \textit{uniformly convex}.
\end{remark}

@@

\section{Application to Poker: Kuhn Poker}
The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
$A = \left[\begin{array}{ccccccccccccc}
  &   &   &   &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
\end{array}\right]$,\\
$E_1 = \left[\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
\end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
and $E_2 = \left[\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
\end{array}\right]$.\\
The pair $(x^*, y^*)$ of realization plans given by\\
$x^* = [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725]^T$ and
$y^* = [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T$ is a Nash equlibrium for the game, computed using Algorithm  \ref{Tab:algo_simplified}. The convergence curve is shown in Fig \ref{Tab:conv_curves}. One easy checks that this equilibrium is feasible. Indeed,  $E_1x^* - e_1 = [4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67 \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, -8.62 \times 10^{-7}, -1.96 \times 10^{-5}]^T$ and $E_2y^* - e_2 = [-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29 \times 10^{-6}, -1.50 \times 10^{-6}, 2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times 10^{-7}]^T$. Finally, $x^*TAy^* = -0.055593685705289997$, which agrees to 4 d.p with the value of $-1 / 18$ computed analytically by Kuhn in his 1954 paper.

@@

\section{Extending to games with more general strategy profiles of a similar type}
Notice tha in \eqref{eq:poly}, the strategy profile of player $k$ can be factored as
\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k}_+| E_kz = e_k\text\}
\end{equation}

The framework presented sofar only demanded we be able to efficiently compute metric projections onto the nonnegative orthant $\mathbb{R}^{n_k}_+$, namely nonnegative clipping. This opens perspectives to envisage general two-person zero sum games for which the players' strategy profiles are of the form
\begin{equation}
  Q_k := \{z \in C_k| E_kz = e_k\text\}
  \label{eq:q_gen}
\end{equation}
where the $C_k$ are arbitrary convex sets for which the metric projections $\Pi_{C_k}$ can be effectively computed.
% \paragraph{Example: Computing best response strategies}

As a motivating example, suppose Alice knows a prior that Bob is playing given realization plan $y_0 \in Q_2$ (for example, take $y_0 = [1, 0, ..., 0]^T \in \mathbb{R}^{n_2}$). Alice seeks a \textit{best response strategy}, namely a strategy $x^* \in Q_1$ such that
\begin{equation}
  x^TAy_0 \le {x^*}^TAy_0,\text{ } \forall x \in Q_1
\end{equation}

One observes that this problem is an instance of problem \eqref{eq:opt_pb} with
$Q_2 = \{y_0\} = \{z \in C_2| E_2z = e_2\text\}$ and $C_2 = \{y_0\}$. Of course the metric projection on $C_2$ is simply the constant map $y \mapsto y_0$.

As another motivating example, suppose we know the support ...
We have the following generalization of Theorem \ref{thm:pd}.

\begin{theorem}
  The Nash equilibrium problem \eqref{eq:opt_pb} with strategy profiles given by  equation \eqref{eq:q_gen}, can be re-written in the equivalent unconstrained form
